Databrary: A digital data library for sharing research video

### 2015-01-26 jcdl-15/paper.tex
combine annotations section, leaving a little in a messy state

\subsubsection*{Simple annotations}

%%dg this feels like it might be padded a little bit.
Once the timeframe of a session is established, this allows temporally-positioned annotations to be attached to the session.
In addition to the structured and organizational annotations discussed in the next section, we currently support simple keyword-based tagging and comment-based discussions on any temporal segment of a session.
Such annotations can also be added through our API by automated video analysis according to features of interest identified in the data.
In addition to enriching datasets and enabling dialog between researchers, we expect these annotations to provide an index target for additional discovery capabilities for users looking for particular features within data \cite{Lanagan_Smeaton_2012}.

@@

\subsubsection*{Structured annotations}
%%dg - might confuse the audience a bit in the difference betweetn simple and structured annotations
Finally, records can be attached not only to entire sessions, but also to arbitrary temporal sub-sets of a session.
That is, if any record only applies to part of a session, such as a single scene or section---for example a participant being present for only part of a recording---it can be applied within the timeline of a session to only the appropriate part.
This allows the final type of organizational structure, wherein records define virtual sub-sessions that can be grouped and interacted with as units, without needing to cut up source videos.
It also can be used to represent annotations at a finer temporal scale, for example individual trials or events that are normally handled by off-line annotation software.
However, the appropriate interfaces and tools to input or import these annotations are still being developed.

@@

%%dg is any of the following redundant with the annotation discussion above?
Another important source for search targets comes from annotations supplied both by the original researchers during analysis as well as by the community.
In the former case, normalization remains a concern, as most annotation schemes researchers employ involve opaque, symbolic or numeric codes with little semantic content.
We are currently working to support import and export workflows for existing annotations tools that will be able to add meaningful definitions to these codes while researchers continue their current practices.
Beyond that, we also plan to build a new, more efficient and structured annotation web interface enabling more of the analysis workflow directly within our system
In this way, Databrary will allow researchers to work with their recordings directly in raw form without having to transfer or transform them, while also capturing more meaningful and standardized contextual information from this process.

>>>>

@@

\subsubsection*{Annotations}

%%dg - note on this section: 1) we can add tags to sessions and portions of sections 2) in adding tags to portions of sessions, we should be able to import data from desktop coding software as tags on portions of sessions.

%%simple
The establishing a timeline for each session allows temporally-positioned, simple annotations to be attached to that session.
In addition to the structured and organizational annotations discussed in the next section, we currently support simple keyword-based tagging and comment-based discussions on any temporal segment of a session.
Such annotations can also be added through our API by automated video analysis according to features of interest identified in the data.
In addition to enriching datasets and enabling dialog between researchers, we expect these annotations to provide an index target for additional discovery capabilities for users looking for particular features within data \cite{Lanagan_Smeaton_2012}.

%%structured
Yet to be implemented is the ability to add structured annotations to sections of a session. Records can be attached not only to entire sessions, but also to arbitrary temporal sub-sets of a session.
If any record only applies to part of a session, such as a single scene or section---for example a participant being present for only part of a recording---it can be applied within the timeline of a session to only that appropriate part.
This allows the final type of organizational structure, wherein records define virtual sub-sessions that can be grouped and interacted with as units, without needing to cut up source videos. %might need to refit this idea in
It also can be used to represent annotations at a finer temporal scale, for example individual trials or events that are normally handled by off-line annotation software.
However, the appropriate interfaces and tools to input or import these annotations are still being developed.

@@

Another important source for search targets would come from annotations supplied both by the original researchers during analysis as well as by the community.
In the former case, normalization remains a concern, as most annotation schemes researchers employ involve opaque, symbolic or numeric codes with little semantic content.
We are currently working to support import and export workflows for existing annotations tools that will be able to add meaningful definitions to these codes while researchers continue their current practices.
Beyond that, we also plan to build a new, more efficient and structured annotation web interface enabling more of the analysis workflow directly within our system
In this way, Databrary will allow researchers to work with their recordings directly in raw form without having to transfer or transform them, while also capturing more meaningful and standardized contextual information from this process.
